---
title: "HW12"
author: '110078509'
date: '20220508'
output:
  html_document: default
  pdf_document: default
  word_document: default
---
```{r setup, include=FALSE} 
#rm(list=ls()) 
knitr::opts_chunk$set(echo = TRUE) 
library(tidyverse) 
library(ggplot2) 
library(car)
boot_mediation <- function(model1, model2, dataset) {
boot_index <- sample(1:nrow(dataset), replace=TRUE)
data_boot <- dataset[boot_index, ]
regr1 <- lm(model1, data_boot)
regr2 <- lm(model2, data_boot)
return(regr1$coefficients[2] * regr2$coefficients[2])
}
```
Create a data.frame called cars_log with log-transformed columns for mpg, weight, and acceleration
(model_year and origin don’t have to be transformed)


### Question 1

#### a. Let’s visualize how weight might moderate the relationship between acceleration and mpg:

ai. Create two subsets of your data, one for light-weight cars (less than mean weight) 
and one for heavy cars (higher than the mean weight)
HINT: consider carefully how you compare log weights to mean weight

```{r}
cars <- read.table("auto-data.txt", header=F, na.strings = "?")
names(cars) <- c("mpg", "cylinders", "displacement", "horsepower", "weight", 
                 "acceleration", "model_year", "origin", "car_name")

cars_log.2 <- with(cars, data.frame(log(mpg),log(cylinders),log(displacement),log(horsepower), log(weight), log(acceleration), model_year, origin))

cars_log <- with(cars, data.frame(log(mpg), log(weight), log(acceleration), model_year, origin))


carmean<-mean(cars_log$log.weight.)

light <- subset(cars_log, log.weight.<carmean, na.action=na.exclude)
heavy <- subset(cars_log, log.weight.>carmean, na.action=na.exclude)
```

aii. Create a single scatter plot of acceleration vs. mpg, with different colors and/or shapes for light versus heavy cars


```{r}
with(light, plot(log.acceleration.,xlim=c(2.2,3.25) ,ylim = c(2.2,3.8), log.mpg., pch=20, col=3, main='Single Scatter Plot of Acceleration vs. MPG.'))

with(heavy, points(log.acceleration., log.mpg., pch=17, col=8))

legend('topright', legend=c("light", "heavy"),
        pch=c(20,17), cex=0.85, col=c(3,8))

```


aiii. Draw two slopes of acceleration-vs-mpg over the scatter plot: 

one slope for light cars and one slope for heavy cars (distinguish them by appearance)


```{r}
with(light, plot(log.acceleration., log.mpg.,xlim=c(2.2,3.25),ylim=c(2.2,3.8), pch=20, col=3, main='Single Scatter Plot of Acceleration vs. MPG.'))

with(heavy, points(log.acceleration., log.mpg., pch=17, col=8))
abline(lm(log.mpg. ~ log.acceleration., data=light), col=3, lwd=2)
abline(lm(log.mpg. ~ log.acceleration., data=heavy), col=8, lwd=2, lty=2)

legend('topright', legend=c("light", "heavy"), pch=c(20,17), cex=0.85,col=c(3,8))
```

#### b.	Report the full summaries of two separate regressions for light and heavy cars where

- Ans: 


```{r}
light<-na.omit(light)
heavy<-na.omit(heavy)

print('Light:')
light.lm <- lm(light$log.mpg.~light$log.weight.+light$log.acceleration.+light$model_year+factor(light$origin))
summary(light.lm)

print('----------------------------BLOCK----------------------------------------')

print('Heavy:')
heavy.lm <- lm(heavy$log.mpg.~heavy$log.weight.+heavy$log.acceleration.+heavy$model_year+factor(heavy$origin))
summary(heavy.lm)
```


#### c.	(not graded) Using your intuition only: What do you observe about light versus heavy cars so far?

- Ans: 

log.acceleration. is only significant(at 0.1 significant.) in 'Light'.


### Question 2

#### a. (not graded) Between weight and acceleration ability, use your intuition and experience to state which variable might be a moderating versus independent variable, in affecting mileage.

```{r}
summary(lm(log.mpg. ~ log.weight. + log.acceleration. + model_year + factor(origin), data=cars_log))
```
Personally, I guessed "log.weight." could be the moderator because it's slope is steeper than the "log.acceleration."'s.

For example, assuming we're testing the performance of the student adopt different learning platforms. In the example case like this , the "original academic performance" could be a strong moderator. Because the students who have a better original academic performance are more likely to have a strong learning ability. And in this case, the relationship between the "original academic performance (moderator)" & "performance after adopt learning platform (Y)"  could be highly correlative, which the slope could be steeper.

#### b. Use various regression models to model the possible moderation on log.mpg.:

(use log.weight., log.acceleration., model_year and origin as independent variables)

bi. Report a regression without any interaction terms
```{r}
summary(lm(log.mpg. ~ log.weight. + log.acceleration. + model_year +factor(origin), data=cars_log))

```

bii. Report a regression with an interaction between weight and acceleration


```{r}
summary(lm(log.mpg.~log.weight.+ log.acceleration. + log.weight.*log.acceleration.+ model_year + factor(origin), data=cars_log))

```

biii. Report a regression with a mean-centered interaction term


```{r}

slw <- scale(cars_log$log.weight., center=TRUE, scale=FALSE)
sla <- scale(cars_log$log.acceleration., center=TRUE, scale=FALSE)


summary(lm(log.mpg. ~ slw + sla +model_year + factor(origin)+ slw*sla, data=cars_log ))

```

----

biv.	Report a regression with an orthogonalized interaction term

```{r}

# Residuals of interaction’s regression

log.weight_x_log.acceleration. <- cars_log$log.weight.*cars_log$log.acceleration.
interaction_regr <- lm(log.weight_x_log.acceleration. ~ cars_log$log.weight.+cars_log$log.acceleration.)

interaction_ortho <- interaction_regr$residuals
#Correlation of residual
#round(cor(cbind(dep, interaction_ortho)), 2)

summary(lm(log.mpg.~ log.weight. + log.acceleration.+ model_year + factor(origin) + interaction_ortho, data=cars_log))
```
#### c. For each of the interaction term strategies above (raw, mean-centered, orthogonalized) what is the correlation between that interaction term and the two variables that you multiplied together?


- Raw

```{r}
# raw
weight_acce_raw <- cars_log$log.weight. * cars_log$log.acceleration.


round(cor(cbind(cars_log[1:3],weight_acce_raw)), 2)
```
- Mean-centered
```{r}
# mean-centered
mean.center = cbind(cars_log$log.mpg., slw, sla, slw*sla)
colnames(mean.center) = c('log.mpg','scale_log.weight', 'scale_log.acceleration','interaction_term' )

round(cor(mean.center), 2)
```

- Orthogonalized

```{r}
# orthogonalized
round(cor(cbind(cars_log[1:3], interaction_ortho)), 2)

```



### Question 3-  Mediator


#### a.i.	Model 1: Regress log.weight. over log.cylinders. only
(check whether number of cylinders has a significant direct effect on weight)


- Ans:

Yes, the log.cylinders. has a significant direct effect on log.weight. (p value < 0.05)

```{r}
cars_log.2 <- with(cars, data.frame(log(mpg), log(cylinders), log(displacement), log(horsepower), log(weight), log(acceleration), model_year,factor(origin)))
cars_log.2<-na.omit(cars_log.2)

model1 <-lm(log.weight.~log.cylinders., data= cars_log.2)
summary(model1)
```



#### aii.	Model 2: Regress log.mpg. over log.weight. and all control variables (check whether weight has a significant direct effect on mpg with other variables statistically controlled?)


- Ans:

```{r}

model2 <- lm(log.mpg. ~ log.weight.+log.acceleration.+model_year + factor(factor.origin.) , data = cars_log.2)
summary(model2)

```

#### b. What is the indirect effect of cylinders on mpg? (use the product of slopes between model 1 & 2)


```{r}
indirect_effect_mpg.cylinder <- model1$coefficients[2]*model2$coefficients[2]
sprintf("The indirect Effect approximately equal to  %.2f", indirect_effect_mpg.cylinder)
```


#### c.	Let’s bootstrap for the confidence interval of the indirect effect of cylinders on mpg

bi.	Bootstrap regression models 1 & 2, and compute the indirect effect each time: 
what is its 95% CI of the indirect effect of log.cylinders. on log.mpg.?


```{r}
set.seed(74)
indirect<-replicate(2000,boot_mediation(model1,model2,cars_log.2))
quantile(indirect, probs=c(0.025, 0.975))
```


bii.	Show a density plot of the distribution of the 95% CI of the indirect effect

```{r}

plot(density(indirect),lwd=2,col="blue", main='Bootstrapping of Indirect Effect')
abline(v=mean(indirect), lty=2, col="red", lwd=2)
abline(v=quantile(indirect, probs=c(0.025, 0.975)), lty=2, lwd=2, col="green")

```


```{css, echo=FALSE}
h2 {
  font-size: 32px;
  color: red !important;
}
```
